---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r}
#load all the required packages
library(ggplot2)
library(tidyverse)
library(ggrepel)
```

First, reading all the files into R
```{r}
sicap0 = read.delim("0min-processed.txt")
sicap4 = read.delim("4min-processed.txt")
sicap8 = read.delim("8min-processed.txt")
sicap12 = read.delim("12min-processed.txt")
coIP = read.delim("coIP-processed.txt")
```


```{r}
rownames(sicap0) = sicap0$Gene.Symbol
rownames(sicap4) = sicap4$Gene.Symbol
rownames(sicap8) = sicap8$Gene.Symbol
rownames(sicap12) = sicap12$Gene.Symbol
rownames(coIP) = coIP$Gene.Symbol
```


```{r}
#save the RDS objects
saveRDS(coIP, "Robjects/coIP.rds")
saveRDS(sicap0, "Robjects/sicap0.rds")
saveRDS(sicap4, "Robjects/sicap4.rds")
saveRDS(sicap8, "Robjects/sicap8.rds")
saveRDS(sicap12, "Robjects/sicap12.rds")
```


```{r}
group = c("PRDM9", "HELLS", "DEK", "SMARCA5","ZC3H13", "FUS")
coIP$style = ifelse(rownames(coIP) %in% group, "red", "black")
sicap0$style = ifelse(rownames(sicap0) %in% group, "red", "black")
sicap4$style = ifelse(rownames(sicap4) %in% group, "red", "black")
sicap4$x <- seq.int(nrow(sicap4))
df = sicap4 %>% filter(sicap4$Gene.Symbol %in% group) 
df$alpha = 1
sicap8$style = ifelse(rownames(sicap8) %in% group, "red", "black")
sicap12$style = ifelse(rownames(sicap12) %in% group, "red", "black")
```


```{r}
#group = c("PRDM9", "HELLS", "DEK", "SMARCA5","ZC3H13", "FUS")
ggplot(sicap0,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = style)) + geom_point(size = 2.5, colour = sicap0$style) + xlim(0,600) + ylim(0,30) geom_text_repel(aes(label= Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1, hjust=1) + ylab("Sum PEP score") + xlab("Decreasing order of enrichment n = 600") + theme_bw() + ggtitle("0 min SICAP")

sicap0$x = seq.int(nrow(sicap0))
ggplot(sicap0,aes(x = x, y=Sum.PEP.Score, alpha = style)) +
  geom_point(size = 2.5, colour = sicap0$style) + 
  xlim(0,600) + ylim(0,30) + ggtitle("0 min SICAP") + 
  geom_text_repel(data = subset(sicap0, style == "red"), 
                  aes(label = Gene.Symbol), vjust = 0.5)+ 
  ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 600") + theme(legend.position = "none") + theme_bw()
```

```{r}
ggplot(sicap4,aes(x = x, y=Sum.PEP.Score, alpha = style)) +
  geom_point(size = 2.5, colour = sicap4$style) + 
  xlim(0,300) + ylim(0,22) + ggtitle("4 min SICAP") + 
  geom_text_repel(data = subset(sicap4, style == "red"), 
                  aes(label = Gene.Symbol), vjust = 1.8)+ 
  ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 253") + theme(legend.position = "none") + theme_bw()

#ggplot(sicap4,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = style)) + geom_point(size = 2.5, colour = sicap4$style) + xlim(0,300) + ylim(0,22) + ggtitle("4 min SICAP") + geom_text_repel(data = subset(sicap4, style == "red"), aes(label = Gene.Symbol))+ ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 253") + theme_bw()

#ggplot(sicap4,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = style)) + geom_point(size = 2.5, colour = sicap4$style) + xlim(0,300) + ylim(0,25) + ggtitle("4 min SICAP") + geom_text_repel(aes(label = (ifelse(sicap4$style == "red", Gene.Symbol,""))), position = "identity", box.padding = 0.25, label.padding = 0.5,max.overlaps = Inf, hjust = 2.0, vjust=1.5) + ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 253") + theme_bw()

#label = ifelse(sicap4$style == "red", Gene.Symbol,"")
#sicap4 %>% filter(style == "red") %>% pull(Gene.Symbol)
#geom_text_repel(aes(label= Gene.Symbol)
```


```{r}
ggplot(sicap8,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = style)) + geom_point(size = 2.5, colour = sicap8$style) + xlim(0,600) + ylim(0,30) + ggtitle("8 min SICAP") + geom_text_repel(aes(label=Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1.2, hjust=1.2) + ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 160") + theme_bw()

sicap8$x = seq.int(nrow(sicap8))
ggplot(sicap8,aes(x = x, y=Sum.PEP.Score, alpha = style)) +
  geom_point(size = 2.5, colour = sicap8$style) + 
  xlim(0,200) + ylim(0,10) + ggtitle("8 min SICAP") + 
  geom_text_repel(data = subset(sicap8, style == "red"), 
                  aes(label = Gene.Symbol), vjust = 1.8)+ 
  ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 160") + theme(legend.position = "none") + theme_bw()
```

```{r}
ggplot(sicap12,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = style)) + geom_point(size = 2.5, colour = sicap12$style) + xlim(0,600) + ylim(0,30) + ggtitle("12 min SICAP") + geom_text_repel(aes(label=Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1.2, hjust=1.2) + ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 357") + theme_bw()

sicap12$x = seq.int(nrow(sicap12))
ggplot(sicap12,aes(x = x, y=Sum.PEP.Score, alpha = style)) +
  geom_point(size = 2.5, colour = sicap12$style) + 
  xlim(0,400) + ylim(0,25) + ggtitle("12 min SICAP") + 
  geom_text_repel(data = subset(sicap12, style == "red"), 
                  aes(label = Gene.Symbol), vjust = 0.4)+ 
  ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 357") + theme(legend.position = "none") + theme_bw()
```

```{r}
ggplot(coIP,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = style)) + geom_point(size = 2.5, colour = coIP$style) + xlim(0,600) + ylim(0,300) + ggtitle("coIP") + geom_text_repel(aes(label=Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1, hjust=1) + ylab("Sum PEP score") + xlab("Decreasing order of enrichment n = 509") + theme_bw

coIP$x = seq.int(nrow(coIP))
ggplot(coIP,aes(x = x, y=Sum.PEP.Score, alpha = style)) +
  geom_point(size = 2.5, colour = coIP$style) + 
  xlim(0,600) + ylim(0,100) + ggtitle("coIP") + 
  geom_text_repel(data = subset(coIP, style == "red"), 
                  aes(label = Gene.Symbol), vjust = 0.5)+ 
  ylab("Sum PEP score") + xlab("Decreasing rank order of enrichment n = 509") + theme(legend.position = "none") + theme_bw()
```

#Load the selected GO nuclear, chromatin terms and plotted them for various SICAP, co-IP timepoints
```{r}
nuclearGO = read.delim("nuclear-chromatinGO.txt", header=FALSE)
riboGO = read.delim("ribo-spliceo-contaminants-GO.txt", header=FALSE)
ribo = as.character(riboGO$V1)

#plotting the coIP,SICAP results and coloring the ribosomal proteins
coIP$GO = ifelse(rownames(coIP) %in% as.character(ribo), "red", "black")
sicap0$GO = ifelse(rownames(sicap0) %in% as.character(ribo), "red", "black")
sicap4$GO = ifelse(rownames(sicap4) %in% as.character(ribo), "red", "black")
sicap8$GO = ifelse(rownames(sicap8) %in% as.character(ribo), "red", "black")
sicap12$GO = ifelse(rownames(sicap12) %in% as.character(ribo), "red", "black")
```


```{r}
ggplot(coIP,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = GO)) + geom_point(size = 2.5, colour = coIP$GO) +xlim(0,600) + ylim(0,100) + ggtitle("coIP GO ribosomal") + ylab("Sum PEP score") + xlab("Decreasing order of enrichment n = 509") + theme_bw() #+ geom_text_repel(aes(label=Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1.2, hjust=2)
```
In the above, plot we can see that lots of ribosomal factors light up but lets see how they look in the SICAP data

First, zero min data
```{r}
ggplot(sicap0,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = GO)) + geom_point(size = 2.5, colour = sicap0$GO) + ylim(0,25) + xlim(0,610) + ggtitle("sicap0 GO ribosomal") + ylab("Sum PEP score") + xlab("Decreasing order of enrichment n = 600") + theme_bw() #+ geom_text_repel(aes(label=Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1, hjust=2.5)
```

Now plotting sicap 4 min data
```{r}
ggplot(sicap4,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = GO)) + geom_point(size = 2.5, colour = sicap4$GO) + xlim(0,600) + ylim(0,25) + xlim(0,250) + ggtitle("sicap4 GO ribosomal") + ylab("Sum PEP score") + xlab("Decreasing order of enrichment n = 253") + theme_bw() #+ geom_text_repel(aes(label=Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1, hjust=2.5)
```

Less ribosomal components show up in SICAP compared to co-IP suggesting specifity

```{r}
ggplot(sicap8,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = GO)) + geom_point(size = 2.5, colour = sicap8$GO) + xlim(0,165) + ylim(0,25) + ggtitle("sicap8 GO ribosomal") + ylab("Sum PEP score") + xlab("Decreasing order of enrichment n = 253") + theme_bw() #+ geom_text_repel(aes(label=Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1, hjust=2.5)
```

```{r}
ggplot(sicap12,aes(x=seq_along(Sum.PEP.Score), y=Sum.PEP.Score, alpha = GO)) + geom_point(size = 2.5, colour = sicap12$GO) + ylim(0,25) + xlim(0,600) +ggtitle("sicap12 GO ribosomal") + ylab("Sum PEP score") + xlab("Decreasing order of enrichment n = 253") + theme_bw() #+ geom_text_repel(aes(label=Gene.Symbol), box.padding = 0.5, max.overlaps = Inf,vjust=1, hjust=2.5)
```
Lets create a table of intersections with ribosomal and spliceomal proteins
```{r}
#already done in excel
```


```{r}
union_sicap_048 = unique(union(sicap0$Gene.Symbol, union(sicap4$Gene.Symbol, sicap8$Gene.Symbol)))
union_sicap = unique(union(union_sicap_048, sicap12$Gene.Symbol))
library(data.table)
fwrite(list(union_sicap), file= "sicap_proteinsUnion.txt")
```


```{r}
#plot the proportion & percentages of spliceosomal and ribosomal hits across various samples
library(datapasta)
hits = data.frame(
  stringsAsFactors = FALSE,
            Sample = c("SICAP0", "SICAP4", "SICAP8", "SICAP12", "coIP"),
          Ribosome = c(44L, 27L, 16L, 36L, 93L),
       Spliceosome = c(40L, 24L, 12L, 31L, 74L),
            Others = c(516L, 202L, 132L, 290L, 342L)
       )

hits_long = reshape2::melt(hits, value.name = "sample")
```


```{r}
# Create ggplot2 plot scaled to 1.00
ggp = ggplot(hits_long,
       aes(x = Sample,
           y = sample,
           fill = variable)) +
  geom_bar(position = "fill", stat = "identity") + ylab("Proportion of hits") + xlab("Sample") + scale_fill_discrete(name = "Protein Classes") + theme_bw()
ggp

#trying to make a plot with raw numbers
ggplot(hitslong,
       aes(x = Sample,
           y = n,
           fill = variable, 
           cumulative = TRUE)) +
  geom_col() +
  geom_text(aes(label = n), 
            position = position_stack(vjust = 0.5)) + 
  ylab("Number of interactors") +
  theme_bw() + 
  scale_fill_discrete(name = "Protein Classes")
```


```{r}
#plotting the proportions scaled to 1
ggplot(hitslong,
       aes(x = Sample,
           y = proportion,
           fill = variable, 
           cumulative = TRUE)) +
  geom_col() +
  geom_text(aes(label = paste0(round(proportion,3))), 
            position = position_stack(vjust = 0.5)) + 
  ylab("Number of interactors") +
  theme_bw() + 
  scale_fill_discrete(name = "Protein Classes")
```


```{r}
# Draw ggplot2 plot scaled to 100%
ggp + ylab("Percentage of hits") + 
  scale_y_continuous(labels = scales::percent_format())

#trying to add percentages to the plot
hitslong = hits_long %>% group_by(Sample,variable) %>% tally(sample) %>% mutate(proportion = n/sum(n))

ggplot(hitslong,
       aes(x = Sample,
           y = proportion * 100,
           fill = variable, 
           cumulative = TRUE)) +
  geom_col() +
  geom_text(aes(label = paste0(round(proportion * 100,1), "%")),
            position = position_stack(vjust = 0.5)) + 
  ylab("Percentage of hits") +
  theme_bw() + 
  scale_fill_discrete(name = "Protein Classes")

```





